Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2020-10-27 paper/main.tex
fix background

Permutations are defined as bijections of the set $[n]$ of integers onto itself. The set of all permutations of $n$ items is denoted as $S_n$ and has cardinality $n!$. We represent permutations as an ordered vector and, following the standard convention, we say that item $i$ is ranked at position $j$ whenever $\sigma(i)=j$. We denote permutations with Greek letters with exception of the identity permutation denoted as $e=(1, 2, 3, \dotsc,n)$. We denote the composition of $\sigma$ and $\pi$ as $\sigma\pi$ and the inverse of $\sigma$ as $\sigma^{-1}$, for which the relation $\sigma\sigma^{-1}=e$ always holds.

@@

The Borda ranking of a sample of permutations $S \subset S_n$ is computed as follows. 
First, for each position $i \in [n]$, compute its Borda score $B(i) =  \sum_{t\in S}  \sigma_t(i)$. Then, assign label 1 to the position with the smallest Borda score, label 2 to the position with the second smallest score and so on, i.e., order the positions by Borda score increasingly.

>>>>

Permutations are defined as bijections of the set $[n]$ of integers onto itself. The set of all permutations of $n$ items is denoted as $S_n$ and has cardinality $n!$. We represent permutations as an ordered vector and, we say that position $i$ contains value $j$ whenever $\sigma(i)=j$. We denote permutations with Greek letters with exception of the identity permutation denoted as $e=(1, 2, 3, \dotsc,n)$. We denote the composition of $\sigma$ and $\pi$ as $\sigma\pi$ and the inverse of $\sigma$ as $\sigma^{-1}$, for which the relation $\sigma\sigma^{-1}=e$ always holds.

@@

The Borda ranking of a sample of permutations $S \subset S_n$ is computed as follows. 
First, for each item $i \in [n]$, compute its Borda score $B(i) =  \sum_{t\in S}  \sigma_t(i)$. Then, assign label 1 to the item with the smallest Borda score, label 2 to the item with the second smallest score and so on, i.e., order the positions by Borda score increasingly.
